Stage-Splitting a Modal Language

### 2014-06-08 paper/splitting.tex
fixed the build and made figures files
added new code examples for future explanatory use
added missing rules
fixed example (no pdf commit)

%\begin{figure*}
%\caption{Type Splitting}
%\label{fig:typeSplit}
%\begin{mathpar}
%\infer [\mathrm{unit}\tsplito]	{\rmunit \tsplito [\rmunit,\rmunit]}{\cdot} \and
%\infer [\mathrm{int}\tsplito]	{{\rm int} \tsplito [{\rm int}, \rmunit]}{\cdot} \and
%\infer [\mathrm{bool}\tsplito]	{{\rm bool} \tsplito [{\rm bool}, \rmunit]}{\cdot} \and
%\infer [\times\tsplito]
%	{A\times B \tsplito [A_1 \times B_1, A_2 \times B_2]}
%	{A \tsplito [A_1, A_2] & B \tsplito [B_1,B_2]} \and
%\infer [\fut\tsplito]
%	{\fut~A \tsplito [{\rm unit}, A']}
%	{A \tsplits A'} \and
%\end{mathpar}
%\end{figure*}
%
%\begin{figure*}
%\caption{Value Splitting}
%\label{fig:valSplit}
%\begin{mathpar}
%\infer [\rmunit\vsplito]		{() \vsplito [(), ()]}{\cdot} \and
%\infer [\mathrm{int}\vsplito]	{i \vsplito [i,()]}{\cdot} \and
%\infer [\mathrm{bool}\vsplito]	{b \vsplito [b,()]}{\cdot} \and
%\infer [\times\vsplito]	
%	{\valprod{v_1}{v_2} \vsplito [\valprod{u_1}{u_2}, \valprod{w_1}{w_2}]}
%	{v_1 \vsplito [u_1,w_1] & v_2 \vsplito [u_2,w_2]} \and
%\infer [\fut\vsplito]
%	{\valnext~v \vsplito [(),v']}
%	{v \vsplits v'} 
%\end{mathpar}
%\end{figure*}
%
%\begin{figure*}
%\caption{Context Splitting}
%\label{fig:contSplit}
%\begin{mathpar}
%\infer {\emptyC \csplit [\emptyC~;~\emptyC]}{\cdot} \and
%\infer {\Gamma, v : A^\bbone \csplit [\Gamma_1,v:A_1; \Gamma_2,v:A_2]}{\Gamma \csplit [\Gamma_1; \Gamma_2] & A \tsplito [A_1, A_2]} \and
%\infer {\Gamma, v : A^\bbtwo \csplit [\Gamma_1; \Gamma_2,v:A']}{\Gamma \csplit [\Gamma_1; \Gamma_2] & A \tsplits A'} 
%\end{mathpar}
%\end{figure*}

\begin{figure*}
\begin{mathpar}
\infersplitone [unit]			{\spl {()}{\rmunit}{((),()),\_.()}}															{\cdot} \and
\infersplittwo [unit]			{\spl {()}{\rmunit}{(),\_.()}}																{\cdot} \and
\infersplitone [int]			{\spl {i}{\rm int}{(i,()),\_.()}}															{\cdot} \and
\infersplittwo [int]			{\spl {i}{\rm int}{(),\_.i}}																	{\cdot} \and
\infersplitone [\times I] 	{\spl {(e_1,e_2)}{A\times B}
									{ \begin{array}{l}
									\left(
										\letin{(y_1,z_1)}{c_1}{\letin{(y_2,z_2)}{c_2}{
										((y_1, y_2),(z_1, z_2))}}
									\right), \\
									(l_1,l_2).(r_1,r_2)
									\end{array}}}																				{\sub 1 A & \sub 2 B} \and
\infersplittwo [\times I]	{\spl {(e_1,e_2)}{A\times B}{(p_1,p_2),(l_1,l_2).(r_1,r_2)}}								{\sub 1 A & \sub 2 B} \and
\infersplitone [\times E_1]	{\spl {\pio~e}{A}{\letin{(y,z)}{c}{(\pio~y,z)},l.\pio~r}}								{\sub {} {A\times B}} \and
\infersplitone [\times E_2]	{\spl {\pit~e}{B}{\letin{(y,z)}{c}{(\pit~y,z)},l.\pit~r}}								{\sub {} {A\times B}} \and
\infersplittwo [\times E_1]	{\spl {\pio~e}{A}{p,l.\pio~r}}																{\sub {} {A\times B}} \and
\infersplittwo [\times E_2]	{\spl {\pit~e}{B}{p,l.\pit~r}}																{\sub {} {A\times B}} \and
\infersplitone [hyp]			{\spl {v}{A}{(x,()),\_.()}}																	{\col x A \in \Gamma} \and
\infersplittwo [hyp]			{\spl {v}{A}{(),\_.x}}																		{\col x A \in \Gamma} \and
\infersplitone [let]			{\spl {\letin{x}{e_1}{e_2}}{B}{
								\begin{array}{l}
									\left(\talllet{(x,z_1)}{c_1}{
									\talllet{(y,z_2)}{c_2}{
									(y, (z_1, z_2))}}\right), \\
									(l_1,l_2).\letin{x}{r_1}{r_2}
								\end{array}}}																					{\sub 1 A & \sub [,\col{x}{A}] 2 B} 		\and
\infersplittwo [let]			{\spl {\letin{x}{e_1}{e_2}}{B}{(p_1,p_2), (l_1,l_2).\letin{x}{r_1}{r_2}}}				{\sub 1 A & \sub [,\col{x}{A}] 2 B} 		\and
\infersplitone [\fut I]		{\spl {\next~e}{\fut A}{((),p),l.r}}														{\splittwosub {} A} 							\and
\infersplittwo [\fut E]		{\spl {\prev~e}{A} {\pit~c,l.r}}															{\splitonesub {} {\fut A}} 					\and
\infersplitone [if]			{\spl {\left( \tallif {e_1}{e_2}{e_3} \right)}{A} 
								{\begin{array}{l}
									\left(\talllet{(y_1,z_1)}{c_1}{\tallif {y_1}
										{\letin{(y_2,z_2)}{c_2}{(y_2, (z_1, \inl~z_2))}}
										{\letin{(y_3,z_3)}{c_2}{(y_3, (z_1, \inl~z_3))}}}
									\right), \\
									(l_1,l_b).(r_1;\caseof{l_b}{l_2.r_2}{l_3.r_3})
								\end{array}}}																					{\sub 1 \rmbool & \sub 2 A & \sub 3 A }		\and
\infersplittwo [if]			{\spl {\left(\tallif {e_1}{e_2}{e_3}\right)}{A} 
								{(p_1,p_2,p_3),(l_1,l_2,l_3).\left(\tallif{r_1}{r_2}{r_2}\right)}}						{\sub 1 \rmbool & \sub 2 A & \sub 3 A }		\and
\end{mathpar}
\caption{Term Splitting}
\label{fig:termSplit}
\end{figure*}

\begin{figure*}
\begin{mathpar}
\infersplitone	 [\to I]	{\spl {\lam{x}{A}{e}}{A \to B}{\vallam{x}{c},
							\_.(\vallam{(x,l)}{r})}}												{\sub [,\col x A] {} B} 									\and
\infersplittwo [\to I]	{\spl {\lam{x}{A}{e}}{A \to B}{p,l.(\vallam{x}{M})}}				{\sub [,\col x A] {} B} 									\and
\infersplitone [\to E]	{\spl {e_1~e_2}{B}{\ldots}}											{\sub 1 {A \to B} & \sub 2 A}							\and
\infersplittwo [\to E]	{\spl {e_1~e_2}{B}{(p_1,p_2),(l_1,l_2).r_1~r_2}}					{\sub 1 {A \to B} & \sub 2 A}							\and
\infersplitone [+ I_1]	{\spl {\inl~e}{A+B}{\letin{(y,z)}{c}{(\inl~y,z)},l.r}}			{\sub {} A}												\and
\infersplitone [+ I_2]	{\spl {\inr~e}{A+B}{\letin{(y,z)}{c}{(\inr~y,z)},l.r}}			{\sub {} A}												\and
\infersplittwo [+ I_1]	{\spl {\inl~e}{A+B}{l.\inl~r}}										{\sub {} A}												\and
\infersplittwo [+ I_1]	{\spl {\inr~e}{A+B}{l.\inr~r}}										{\sub {} A}												\and
\infersplitone [+ E]		{\spl {\left(\tallcase{e_1}{x_2.e_2}{x_3.e_3}\right)}{C}
								{\begin{array}{l}\left(
								\talllet{(y_1,z_1)}{c_1}{
									\tallcase{y_1}
									{x_2.\letin{(y_2,z_2)}{c_2}{(y_2,(z_1,\inl(z_2)))}}
									{x_3.\letin{(y_3,z_3)}{c_3}{(y_3,(z_1,\inr(z_3)))}}
								}\right), \\
								(l_1,l_b).\left(\talllet{z}{r_1}{
									\tallcase{l_b}
									{l_2.\letin{x_2}{z}{r_2}}
									{l_3.\letin{x_3}{z}{r_3}}}\right)\end{array}}}				{\sub 1 {A+B} & \sub [,\col{x_2} A] 2 C 
																									& \sub [,\col{x_3} B] 3 C} 								\and
\infersplittwo [+ E]		{\spl {\left(\tallcase{e_1}{x_2.e_2}{x_3.e_3}\right)}{C}
								{(p_1,p_2,p_3), (l_1,l_2,l_3).\left(\tallcase{r_1}
									{x_2.r_2}{x_3.r_3}\right)}}				{\sub 1 {A+B} & \sub [,\col{x_2} A] 2 C 
																									& \sub [,\col{x_3} B] 3 C} 								\and
\end{mathpar}
\caption{Sum and Function Splitting}
\label{fig:advancedTypes}
\end{figure*}

@@

The theorem that we want to be true is...

%\begin{center}
%\begin{tabular}{l}
%If $\splittwo{e}{A}{p,l.r}$ \\
%and $\reducetwo{e}{v}$ \\
%then $\reduce{p}{u}$ \\
%and $\reduce{[u/l]r}{w}$ \\
%and $v = w$ 
%\end{tabular}
%\end{center}

%\begin{center}
%\begin{tabular}{l}
%If $\splitone {e}{A}{c,l.r}$ \\
%and $\colone {\gamma_1}{\Gamma}$ \\
%and $\coltwo {\gamma_2}{\Gamma}$\\
%and $\rsone{\gamma_1(e)}{v}{q}$ \\
%and $\reducetwo{\gamma_2(q)}{w}$ \\
%then $\reduce{|\gamma_1|(c)}{\valprod{v}{u}}$ \\
%and $\reduce{[u/l]|\gamma_2|(r)}{w}$
%\end{tabular}
%~~~
%\begin{tabular}{l}
%If $\splittwo{e}{B}{p,l.r}$ \\
%and $\colone {\gamma_1}{\Gamma}$ \\
%and $\coltwo {\gamma_2}{\Gamma}$\\
%and $\rstwo{\gamma_1(e)}{q}$ \\
%and $\reducetwo{\gamma_2(q)}{w}$ \\
%then $\reduce{|\gamma_1|(p)}{u}$ \\
%and $\reduce{[u/l]|\gamma_2|(r)}{w}$ 
%\end{tabular}
%\end{center}

@@

\lstset{language=ML, columns=fullflexible, basicstyle=\ttfamily, tabsize=4, escapeinside={"*}{*"}}
\begin{lstlisting} 
let exp (b : $int, e : int) : $int =
	if e == 0 then
		next{1}
	else if (e mod 2) == 0 then
		next{let x = prev{exp(b,e/2)} in x*x}
	else
		next{prev{b} * prev{exp (b,e-1)}}		
\end{lstlisting}

@@

\begin{lstlisting} 
let qs (l : "*$\mathtt{\mu \alpha. }$*"() + "*$\mathtt{int*\alpha}$*", i: $int) = 
	case unroll l of
	  () => next {0}
	| (h,t) => 
		let (left,right,n) = partition h t in
		next{
			let n = prev{hold n} in
			case compare prev{i} n of
			  () (*LT*) => prev {qs left i}
			| () (*EQ*) => hold h
			| () (*GT*) => 
				prev {qs right next{prev{i}-n-1}}
		}	
\end{lstlisting}

>>>>

@@

@@

\begin{lstlisting} 
let exp (b : $int, e : int) : $int =
	if e == 0 then
		next{1}
	else if (e mod 2) == 0 then
		next{let x = prev{exp(b,e/2)} in x*x}
	else
		next{prev{b} * prev{exp (b,e-1)}}		
\end{lstlisting}

@@

\begin{lstlisting} 
let qs (l : "*$\mathtt{\mu \alpha. }$*"() + "*$\mathtt{int*\alpha}$*", i: $int) = 
	case unroll l of
	  () => next {0}
	| (h,t) => 
		let (left,right,n) = partition h t in
		next{
			let n = prev{hold n} in
			case compare prev{i} n of
			  () (*LT*) => prev {qs left i}
			| () (*EQ*) => prev {hold h}
			| () (*GT*) => 
				prev {qs right next{prev{i}-n-1}}
		}	
\end{lstlisting}
